Estimating Information Transfer from Different Data Sources via Precise Bias-variance Asymptotics

### 2021-07-10 revision_journal/multitask.tex
minor edit

\begin{example}[How to set the width $r$ in HPS?]
\label{ex_same_cov}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
An important question in applications of HPS is how to set the width $r$ of the feature layer.
We use our estimates to show that the optimal width depends on the tradeoff between the estimator's bias and variance.
Concretely, consider a random-effect model where all tasks share a model vector $\beta_0$ plus perturbations.
For every $i=1,2,\cdots, t,$, $\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$}, where $\wt \beta^{(i)}$ denotes the $i$-th
%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $\frac {\kappa^2} p$.

>>>>

\begin{example}[How to set the width $r$ in HPS?]
\label{ex_same_cov}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
An important question in applications of HPS is how to set the width $r$ of the feature layer.
We use our estimates to show that the optimal width depends on the tradeoff between the estimator's bias and variance.
Concretely, consider a random-effect model where all tasks share a model vector $\beta_0$ plus perturbations.
For every $i=1,2,\cdots, t,$, $\beta^{(i)} = \beta_0 + \wt \beta^{(i)}$, where $\wt \beta^{(i)}$ denotes the $i$-th task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $\frac {\kappa^2} p$.
